\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-15 article.tex
proper citation for independance and partial correlation
add reference
fig in filtering part

%% Personnal package
\usepackage{enumerate}
\usepackage{bbold}

@@

\title{Connectome inferences using partial correlation from imaging calcium signal}

@@

\textcolor{red}{This section should be rewritten once we get the figure
                which displayed the effect of the different filters.}

@@

@@

If the random variables $X$ follows a joint Gaussian distribution
$p_\mathcal{X} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
covariance matrix $\Sigma$, we have the conditional independence
$X_i \perp X_j | X^{-i,j}$ if the partial correlation coefficient
\[
\rho_{X_i, X_j | X^{-i,j}}
= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}
\]
is equal zero. The partial correlation gives a connectivity score
$\hat{A}: \hat{a}_{i,j} = \rho_{X_i, X_j | X^{-i,j}}, \forall i, j \in V$ between all
pairs of neuron $i$ and $j$. One could retrieve an estimated graph by thresholding
the matrix $\hat{A}$.
Similarly, we also have $X_i \perp X_j$ if the Pearson correlation
coefficient
\[
\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
\Sigma_{jj}}}
\]
is equal to zero.

>>>>

%% Personnal package
\usepackage{enumerate}
\usepackage{bbold}
\usepackage{wrapfig}

@@

\title{\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal}

@@

% \textcolor{red}{This section should be rewritten once we get the figure
                % which displayed the effect of the different filters.}

@@

\begin{wrapfigure}{r}{0.7\linewidth}
\caption{Filtering steps.}\label{wrap-fig:1}
\includegraphics[width=\linewidth]{code/code/fig_filtering.png}
\end{wrapfigure}

@@

If the random variables $X$ follows a joint Gaussian distribution
$p_\mathcal{X} \sim \mathcal{N}(\mu; \Sigma)$ of mean vector $\mu$ and
covariance matrix $\Sigma$, we have the conditional independence
$X_i \perp X_j | X^{-i,j}$ if the partial correlation coefficient
\[
\rho_{X_i, X_j | X^{-i,j}}
= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}}
\]
is equal to zero (\cite{koller2009probabilistic}). The partial correlation gives
a connectivity score
$\hat{A}: \hat{a}_{i,j} = \rho_{X_i, X_j | X^{-i,j}}, \forall i, j \in V$ between all
pairs of neuron $i$ and $j$. One could retrieve an estimated graph by thresholding
the matrix $\hat{A}$.
Similarly, we also have $X_i \perp X_j$ if the Pearson correlation
coefficient
\[
\rho_{X_i,X_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
\Sigma_{jj}}}
\]
is equal to zero.
